\huge Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence $^{*}$\footnoterule\thanks{$^{*}$This work is partially supported by NSF Grant RI-Medium: \#IIS-1162095 to }

### 2015-04-29 Latex files/paper.tex
Edited first 2 pages (abstract to be added)

%\usepackage{cite}      % Written by Donald Arseneau
                        % V1.6 and later of IEEEtran pre-defines the format
                        % of the cite.sty package \cite{} output to follow
                        % that of IEEE. Loading the cite package will
                        % result in citation numbers being automatically
                        % sorted and properly "ranged". i.e.,
                        % [1], [9], [2], [7], [5], [6]
                        % (without using cite.sty)
                        % will become:
                        % [1], [2], [5]--[7], [9] (using cite.sty)
                        % cite.sty's \cite will automatically add leading
                        % space, if needed. Use cite.sty's noadjust option
                        % (cite.sty V3.8 and later) if you want to turn this
                        % off. cite.sty is already installed on most LaTeX
                        % systems. The latest version can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/

@@

The hand-eye calibration problem can be modeled as the $\textbf{AX = XB}$, where $A$s and $B$s are the homogeneous transformation matrices describing the relative motion of the end-effector and the sensor respectively. As shown in Fig.~\ref{fig1}, $A = A^{i}(A^{i+1})^{-1}$ and $B = B^{i}(B^{i+1})^{-1}$. The homogeneous transformation matrix can be described as:
\begin{equation}\label{equ0}
    g(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right)
\end{equation}

@@

Given multiple pairs of $(A_{i},B_{i}) \in SE(3) \times SE(3)$ with correspondence, many methods have been proposed to solve for $X$ including decoupling of rotation and translation, least squares fitting, singular value decomposition (\emph{SVD}), screw theory, nonlinear
optimization, quaternion, gradient descent and interactive approaches \cite{Shiu1989,Tsai1989,Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}. Theses methods assume that there is exact knowledge of the $As$ and $Bs$ correspondence. Considering data streams containing the $A$ and $B$ will be asynchronous that are discussed in many instances
in the literature, several methods regardless of the correspondence or recovering the correspondence between two data sets are presented \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.

Simultaneous estimation of the hand-eye transformation and robot-world one
has been viewed as $\textbf{AX=YB}$ problem. As shown in Fig.~\ref{fig1}, $Y$ is the transformation of the robot base relative to the world, $A$ is the sensor to the world transformation, and $B$ is the hand/end-effector to the robot base rigid transformation. The $A$ and $B$ in $\textbf{AX=YB}$ calibration is different from ones in $\textbf{AX=XB}$ from a physical view. This problem has been studied in different methods such as SVD, closed-form, quaternion and nonlinear optimization \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}. Another approach integrate multiple robots to calibrate hand-eye, tool-flange and robot-robot transformation in $\textbf{AXB=YCZ}$ problem \cite{Wang2014}. Simultaneous solution for $X$ and $Y$ in $\textbf{AX=YB}$ problem is an challenging issue. In the above methods, the correspondence between $A$ and $B$ is known a prior. In this paper, our solution for $\textbf{AX=YB}$ doesn't require a priori knowledge of correspondences.

The rest of the paper is organized as follows. In Section
\ref{sect2} we present the probabilistic theory to solve for $X$ and $Y$. In Section \ref{sect3} a algorithmic solution involving correlation theorem and Euclidean group invariants is posed to recover the correspondence. The simulation results, including known  and unknown correspondence, are illustrated in Section \ref{sect4}. Finally, we draw some conclusions.

@@

Given a large set of pairs $(A_{i},B_{i})\in SE(3)\times SE(3)$ for $i=1,\cdots,n$ that are acquired by measurements and satisfy the following equations

\begin{equation}\label{equ1}
A_{i}X=YB_{i}
\end{equation}

In the case of $SE(3)$, a Dirac delta function, or $\delta$ function, is thought of as a function which is zero everywhere except at the identity where it is infinite.

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{ll}
+\infty, & H=I \\
0, & H \neq I
\end{array}
\right.
\end{equation}

Dirac delta function is also constrained to satisfy the identity.

\begin{equation}\label{equ3}
\int_{SE(3)}\delta{(H)}dH=1
\end{equation}

A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given two functions $f_{1}(g)$ and $f_{2}(g)$, their convolution in Lie group is defined as follows,

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(g)=\int_{SE(3)}f_{1}(h)f_{2}(h^{-1}\circ g)dh
\end{equation}

Considering the properties of $\delta$ function, the following equation is built.

\begin{equation}\label{equ5}
(f\ast \delta)(g)=\int_{SE(3)}f(h)\delta(h^{-1}\circ g)dh=f(g)
\end{equation}

Therefore, for each $A_{i}$ and $B_{i}$ can get

\begin{IEEEeqnarray}{l}\label{equ6}
(\delta_{A_{i}}\ast \delta_{X})(g)=\delta(A_{i}^{-1} g X^{-1}) \IEEEyessubnumber
\\*
(\delta_{Y}\ast \delta_{B_{i}})(g)=\delta(Y^{-1} g B_{i}^{-1}) \IEEEyessubnumber
\end{IEEEeqnarray}

Together with $g=A_{i}X=YB_{i}$, we can obtain the convolution equation

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast \delta_{B_{i}})(g)
\end{equation}

Convolution provides a linear operation on functions with additional properties. We can add up $n$ instances into a single function.

\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}g) \IEEEyessubnumber
\\*
f_{B}(g)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}g) \IEEEyessubnumber
\end{IEEEeqnarray}

Therefore,

\begin{equation}\label{equ9}
(f_{A_{i}}\ast \delta_{X})(g)=(\delta_{Y}\ast f_{B_{i}})(g)
\end{equation}

In each transformation set $A_i$s and $B_i$s, we are using small relative motions between consecutive reference frames. Given a measure of distance between reference frames, e.g.

\begin{eqnarray}\label{equ10}
d^{2}(A_{i},A_{j})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
\end{eqnarray}

we have that  $\Delta A = A_{i}-A_{j}$ and $0 < \epsilon \ll 1 $

The convolution of "highly focused" distributions corresponding to closely clumped sets of reference frames have some interesting properties that we can exploit to solve for $X$. In particular, let the mean and covariance of a probability density, $f(g)$(e.g. $f_{A}(g),f_{B}(g)$), be defined by the conditions.

\begin{IEEEeqnarray}{l}\label{equ11}
\int_{SE(3)}log(M^{-1}g))f(g)dg=0 \IEEEyessubnumber
\\*
\Sigma = \int_{SE(3)}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T}f(g)dg \IEEEyessubnumber
\end{IEEEeqnarray}

A discrete version as for $f_{A}(g)$ is

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}log(M^{-1}g))=0 \IEEEyessubnumber
\\*
\Sigma_{A} = \sum_{i=1}^{n}log^{\vee}(M^{-1}g)[log^{\vee}(M^{-1)}g)]^{T} \IEEEyessubnumber
\end{IEEEeqnarray}

>>>>

\usepackage{cite}      % Written by Donald Arseneau
                        % V1.6 and later of IEEEtran pre-defines the format
                        % of the cite.sty package \cite{} output to follow
                        % that of IEEE. Loading the cite package will
                        % result in citation numbers being automatically
                        % sorted and properly "ranged". i.e.,
                        % [1], [9], [2], [7], [5], [6]
                        % (without using cite.sty)
                        % will become:
                        % [1], [2], [5]--[7], [9] (using cite.sty)
                        % cite.sty's \cite will automatically add leading
                        % space, if needed. Use cite.sty's noadjust option
                        % (cite.sty V3.8 and later) if you want to turn this
                        % off. cite.sty is already installed on most LaTeX
                        % systems. The latest version can be obtained at:
                        % http://www.ctan.org/tex-archive/macros/latex/contrib/supported/cite/

@@

The hand-eye calibration problem can be modeled as the $\textbf{AX = XB}$, where $A$s and $B$s are the homogeneous transformation matrices describing the relative motion of the end-effector and the sensor respectively. As shown in Fig.~\ref{fig1}, $A_{i} = A^{i}(A^{i+1})^{-1}$ and $B_{i} = B^{i}(B^{i+1})^{-1}$. The homogeneous transformation matrix can be described as:
\begin{equation}\label{equ0}
    g(R,t)=\left(
             \begin{array}{cc}
               R & t \\
               0^{T} & 1 \\
             \end{array}
           \right)
\end{equation}

@@

Given multiple pairs of $\{A_{i},B_{i}\} \in SE(3) \times SE(3)$ with correspondence, many methods have been proposed to solve for $X$. To the best of the authors' knowledge, Shiu\cite{Shiu1989} and Tsai\cite{Tsai1989} are the first to solve the $AX=XB$ sensor calibration problem. The other methods include but are not limited to quaternion, dual quaternion, screw theory, Lie group theory, convex optimization and gradient descent methods \cite{Wang1992,Park1994,Horaud1995,Daniilidis1999,Fassi2005,Zhao2011,Ackerman2014a}. All of the methods above assume a prior knowledge of exact correspondence  between $A_{i}$ and $B_{i}$. For data streams $\{A_{i}\}$ and $\{B_{j}\}$ that are asynchronous, several methods have been proposed in the literature to solve for $X$ using data without correspondence \cite{Ackerman2013a,Ackerman2013,Ackerman2014}.

Simultaneous estimation of the hand-eye and robot-world transformations
has been viewed as the $\textbf{AX=YB}$ problem. As shown in Fig.\ref{fig1}, $Y$ is the transformation of the robot base relative to the world frame, $A$ denotes the sensor's pose in the world frame, and $B$ is the transformation of  the end-effector with respect to its fixed base. The $A_{i}$ and $B_{i}$ in $\textbf{AX=YB}$ are different from those in $\textbf{AX=XB}$ which can be seen in Fig.\ref{fig1}. The $\textbf{AX=YB}$ problem has been solved by different methods such as kronecker product, quaternion, dual quaternion, and nonlinear optimization method \cite{Zhuang1994,dornaika1998simultaneous,Hirsh2001, ernst2012non,strobl2006optimal,Li2010,Shah2013,Heller2014}. Simultaneous calibration of $X$ and $Y$ can be problematic in that all the methods above assume exact correspondence between $\{A_{i}\}$ and $\{B_{j}\}$, which is not the case in real experiments. Another similar problem involves the calibration of multiple robots in terms of hand-eye, tool-flange and robot-robot system, and it is formulated as the $\textbf{AXB=YCZ}$ problem \cite{Wang2014}. In this paper, we focus on the $\textbf{AX=YB}$ problem which does not require a priori knowledge of correspondences of the data streams.

The rest of the paper is organized as follows. In Section
\ref{sect2}, we present a probabilistic method to solve for $X$ and $Y$. In Section \ref{sect3}, a algorithmic solution involving both the correlation theorem and Euclidean group invariants is posed to recover the correspondence between $\{A_{i}\}$ and $\{B_{j}\}$. The simulation results which deal with the data streams with both known and unknown correspondence are illustrated in Section \ref{sect4}. Finally, conclusions are drawn based on the numerical results and possible future works are pointed out.

@@

Given a large set of pairs $\{A_{i},B_{i}\}\in SE(3)\times SE(3)$ for $i=1,\cdots,n$ that are acquired by measurements and satisfy the following equation:
\begin{equation}\label{equ1}
A_{i}X=YB_{i}.
\end{equation}
For a matrix $H \in SE(3)$, a Dirac delta function $\delta(H)$ function is defined to be finite only at the identity and zero everywhere else:

\begin{equation}\label{equ2}
\delta{(H)}=
\left\{
\begin{array}{ll}
+\infty, & H=I \\
0, & H \neq I
\end{array}
\right.
\end{equation}
It also satisfies the identity constraint as:
\begin{equation}\label{equ3}
\int_{SE(3)}\delta{(H)}dH=1.
\end{equation}

A shifted Dirac delta function can be defined as $\delta_{A}(H)=\delta{(A^{-1}H)}$. Given $K, H \in SE(3)$ and two functions $f_1, f_2 \in (L^1 \cap L^2)(SE(3))$, their convolution on $SE(3)$ is defined as:

\begin{equation}\label{equ4}
(f_{1}\ast f_{2})(H)=\int_{SE(3)}f_{1}(K)f_{2}(K^{-1}H)dK
\end{equation}
where $h \in SE(3)$. Employing the properties of $\delta$ function, it is straightforward to see that:

\begin{equation}\label{equ5}
(f\ast \delta)(H)=\int_{SE(3)}f(K)\delta(K^{-1}H)dK=f(H).
\end{equation}
Therefore, for each $A_{i}$ and $B_{i}$, we have:

\begin{IEEEeqnarray}{l}\label{equ6}
(\delta_{A_{i}}\ast \delta_{X})(H)=\delta(A_{i}^{-1} H X^{-1}) \IEEEyessubnumber
\\*
(\delta_{Y}\ast \delta_{B_{i}})(H)=\delta(Y^{-1} H B_{i}^{-1}) \IEEEyessubnumber
\end{IEEEeqnarray}
Together with $A_{i}X=YB_{i}$, we can obtain the convolution equation:

\begin{equation}\label{equ7}
(\delta_{A_{i}}\ast \delta_{X})(H)=(\delta_{Y}\ast \delta_{B_{i}})(H)
\end{equation}

Convolution provides a linear operation on functions with addition properties.  After adding up $n$ instances of $\delta_{A_{i}}(H)$ and $\delta_{B_{i}}(H)$, we obtained the following equations:

\begin{IEEEeqnarray}{l}\label{equ8}
f_{A}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(A_{i}^{-1}H) \IEEEyessubnumber
\\*
f_{B}(H)=\frac{1}{n}\sum_{i=1}^{n} \delta(B_{i}^{-1}H) \IEEEyessubnumber
\end{IEEEeqnarray}

Therefore, we have:
\begin{equation}\label{equ9}
(f_{A}\ast \delta_{X})(H)=(\delta_{Y}\ast f_{B})(H).
\end{equation}

For each of the data stream $\{A_i\}$ and $\{B_i\}$, we are using small relative motions between consecutive reference frames. Take $\{A_{i}\}$ for example, one metric of the distance between $A_i$ and $A_j$ can be defined as:

\begin{eqnarray}\label{equ10}
d^{2}(A_{i},A_{i+1})=\parallel \Delta A \parallel_{W}^{2} = trace[(\Delta A)W(\Delta A)^{T}] = \epsilon,\nonumber \\
\end{eqnarray}
where  $\Delta A = A_{i}-A_{j}$ (or $\Delta A = A_{i}^{-1}A_{j}$) and $0 < \epsilon \ll 1 $

The convolution of two ``highly focused" probability density functions (pdf) has some interesting properties that can be used to solve for $X$. In particular, firstly, define the mean $M$ and covariance $\Sigma$ of a probability density function on $SE(3)$ as:

\begin{IEEEeqnarray}{l}\label{equ11}
\int_{SE(3)}log(M^{-1}H))f(H)dH=0 \IEEEyessubnumber
\\*
\Sigma = 
\int_{SE(3)}log^{\vee}(M^{-1}H)[log^{\vee}(M^{-1}H)]^{T}f(H)dH \IEEEyessubnumber
\end{IEEEeqnarray}

Then the corresponding discrete version of $f_{A}(H)$ will be:

\begin{IEEEeqnarray}{l}\label{equ12}
\sum_{i=1}^{n}log(M_{A}^{-1}H))=0 \IEEEyessubnumber
\\*
\Sigma_{A} = \sum_{i=1}^{n}log^{\vee}(M_{A}^{-1}H)[log^{\vee}(M_{A}^{-1)}H)]^{T} \IEEEyessubnumber
\end{IEEEeqnarray}
